Untrusted B2B Collaboration using the Blockchain

### 2018-07-30 paper/paper.tex
Move screencast and small changes

In the following, we will briefly present the tools we implemented integrate process management with our blockchain approach.
The implementations can be found in our repository at \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/}, in the \texttt{armadillo} and \texttt{eth\_admin} folders, respectively.
% TODO repo & hbox

@@

As a way of joining process execution with our blockchain architecture, we developed a single page web application (see Figure \ref{fig:armadillo}) in JavaScript and HTML, using the Vue.js framework\footnote{\url{https://vuejs.org}}.
With the help of the Web3 Ethereum JavaScript API\footnote{\label{web3}\url{https://github.com/ethereum/web3.js/}}, we can trigger contract functions based on user actions in the applications user interface.
Armadillo also implements the upload and rendering of BPMN diagrams using the bpmn.js toolkit\footnote{\url{https://bpmn.io/toolkit/bpmn-js/}}.
Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on \emph{BPMN Service Tasks}, which allowed us to use the viewer as a process engine mock.
A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/blob/master/presentation/armadillo-screencast.mp4}.
% TODO repo, hbox etc.

>>>>

In the following, we will briefly present the tools we implemented integrate process management with our blockchain approach.
The implementation can be found at \url{https://github.com/p-otto/armadillo}, in the \texttt{armadillo} and \texttt{eth\_admin} folders, respectively.

@@

As a way of joining process execution with our blockchain architecture, we developed a single page web application (see Figure \ref{fig:armadillo}) in JavaScript and HTML, using the Vue.js framework\footnote{\url{https://vuejs.org}}.
With the help of the Web3 Ethereum JavaScript API\footnote{\label{web3}\url{https://github.com/ethereum/web3.js/}}, we can trigger contract functions based on user actions in the applications user interface.
Armadillo also implements the upload and rendering of BPMN diagrams using the bpmn.js toolkit\footnote{\url{https://bpmn.io/toolkit/bpmn-js/}}.
Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on \emph{BPMN Service Tasks}, which allowed us to use the viewer as a process engine mock.
A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/armadillo/blob/master/presentation/armadillo-screencast.mp4}.
% TODO repo, hbox etc.
